General purpose gene annotation using deep learning

### 2020-04-13 paper/main.tex
caption

We use metrics two metrics to judge model performance. The {\it Genic F1} is our primary metric that provides the most comprehensive picture of annotation quality in one number. The {\it Subgenic F1} is similar to the Genic F1, except that it does not take UTR predictions into account. This is done for comparability with Augustus and further explained in Chapter \ref{augustus}. Both metrics work by summing up True Positives (TP), False Positives (FP) and False Negatives (FN) of each considered class before calculating precision and recall from these values and combining the two into a F1 score. Both metrics do not take the values of the intergenic class into account, as this class is very abundant and appears to be by far the easiest to predict. In the case of the Genic F1, this means that effectively only the TP of the intergenic class are disregarded. The metrics essentially provide a weighted mean of the performances in the considered classes. All individual class performances are reported in Supplementary Material (?).

@@

\subsection{Evaluation of Augustus} \label{augustus}
What Marvin did, why we don't use Genic F1 for comparison, etc

@@

\begin{figure}[!tpb]
	\centerline{\includegraphics[width=0.45\textwidth]{images/overall_boxplot}}
\caption{Caption, caption.}\label{fig:boxplot}
\end{figure}

\begin{table}[!t]
\processtable{Experimental Results and Comparison\label{tab:results}} {
\begin{tabular}{@{}lll@{}}
\toprule & Animals & Plants\\
\midrule
Augustus & 0.632 (+-0.089) & 0.749 (+-0.161)\\
Dilated CNN Baseline & - (+-) & - (+-)\\
Best Helixer model & - (+-) & - (+-) \\
Best model + varied input length & - (+-) & - \\
Best model (+ varied input length) + overlapping &  0.85 (+-0.068) & 0.843 (+-0.151) \\
(Varied input length +) overlapping + ensembling & 0.868 (+-0.064) & 0.863 (+-0.148) \\
\botrule
\end{tabular}}{Values are the median in Subgenic F1 across all validation and test genomes of the respective group. Varied input length was only used in the animal case. The best model was chosen out of the eight models of the ensemble for having the best performance in the reported setup. The Augustus result is the median score for all genomes.}
\end{table}

>>>>

We use metrics two metrics to judge model performance. The {\it Genic F1} is our primary metric that provides the most comprehensive picture of annotation quality in one number. The {\it Subgenic F1} is similar to the Genic F1, except that it does not take UTR predictions into account. This is done for comparability with AUGUSTUS and further explained in Chapter \ref{augustus}. Both metrics work by summing up True Positives (TP), False Positives (FP) and False Negatives (FN) of each considered class before calculating precision and recall from these values and combining the two into a F1 score. Both metrics do not take the values of the intergenic class into account, as this class is very abundant and appears to be by far the easiest to predict. In the case of the Genic F1, this means that effectively only the TP of the intergenic class are disregarded. The metrics essentially provide a weighted mean of the performances in the considered classes. All individual class performances are reported in Supplementary Material (?).

@@

\subsection{Evaluation of AUGUSTUS} \label{sec:augustus}
What Marvin did, why we don't use Genic F1 for comparison, etc

@@

\begin{figure}[!tpb]
	\centerline{\includegraphics[width=0.45\textwidth]{images/overall_boxplot}}
	\caption{Subgenic F1 scores for all animal and plant genomes that were not used during training of Helixer, which is equivalent to all validation and test genomes. Results are given for Helixer and AUGUSTUS with the median predictions scores being denoted by the red lines. Details of how AUGUSTUS was used are given in Section \ref{sec:augustus}.}\label{fig:boxplot}
\end{figure}

\begin{table}[!t]
\processtable{Experimental Results and Comparison\label{tab:results}} {
\begin{tabular}{@{}lll@{}}
\toprule & Animals & Plants\\
\midrule
AUGUSTUS & 0.632 (+-0.089) & 0.749 (+-0.161)\\
Dilated CNN Baseline & - (+-) & - (+-)\\
Best Helixer model & - (+-) & - (+-) \\
Best model + varied input length & - (+-) & - \\
Best model (+ varied input length) + overlapping &  0.85 (+-0.068) & 0.843 (+-0.151) \\
(Varied input length +) overlapping + ensembling & 0.868 (+-0.064) & 0.863 (+-0.148) \\
\botrule
\end{tabular}}{Values are the median in Subgenic F1 across all validation and test genomes of the respective group. Varied input length was only used in the animal case. The best model was chosen out of the eight models of the ensemble for having the best performance in the reported setup. The AUGUSTUS result is the median score for all genomes.}
\end{table}
